\subsection{Conclusion}
This report has presented the design and implementation of a radio network aimed at maximising coverage within the Himalayan region near Dehradun, India.
The primary objective was to achieve extensive coverage while minimising the required infrastructure.
This report has demonstrated the effectiveness of \textit{Radio Mobile} software in designing and analysing such a network.

\subsubsection{Simulation outcomes and key findings}
\begin{itemize}
    \item Radio Mobile provided a valuable tool for visualising and analysing the coverage area, enabling informed decision-making throughout the design process.
    \item By carefully planning and strategically placing four repeater stations, we were able to achieve an impressive coverage area of \textcolor{Green}{\textbf{98.233\%}}.
\end{itemize}

\subsection{Future Aspects}
While the current network design achieves excellent coverage, there are always opportunities for further improvement and expansion.
\begin{itemize}
    \item As data usage and the number of users within the network grow, the existing infrastructure might need to be upgraded to handle the increased demand. 
    This could involve using higher-bandwidth technologies, and many more \ldots
    \item As demand for reliable communication grows, the network will need to adapt to ensure continued coverage and performance.
    This might involve extending the network to incorporate new areas or enhancing coverage in existing locations with specific needs.
\end{itemize}

Overall, this report demonstrates the successful implementation of a cost-effective and efficient radio network solution.